---
title: "Saving plots"
output: html_document
---

Backfillz allows you to save and recall your backfillz plots.

# Backfillz history 

Here we use the sample MCMC data included in the Backfillz package.

```{r, message=FALSE}
library(backfillz)

x <- as_backfillz(sample_stanfit)
```

Backfillz objects have a history which records the object events, such as creating the object and creating plots. To view the object history either pass the object name to the console

```{r, eval=FALSE}
x
```

or access the history directly.
```{r, eval=FALSE}
x@plot_history
```

```{r, echo=FALSE}
knitr::kable(x@plot_history)
```


# Saving

The Backfillz plot function have the parameter save_plot. Setting this to false will create the plot but will not save the plot in the backfillz object.

```{r, message=FALSE, fig.width=10, fig.height=10}
x <- plot_slice_histogram(x, save_plot = FALSE)
```

The save status of the plot is shown in the object history.

```{r, eval=FALSE}
x@plot_history
```

```{r, echo=FALSE}
knitr::kable(x@plot_history)
```

Change save_plot to try in order to save the plot in the plot object,

```{r, results=FALSE, fig.show='hide', message=FALSE}
x <- plot_slice_histogram(x, save_plot = TRUE)
```

as verified by checking the object history.

```{r, eval=FALSE}
x@plot_history
```

```{r, echo=FALSE}
knitr::kable(x@plot_history)
```


# Recalling

A saved plot can be recalled via the recall_plots function. The function requires the backfillz object and the ID of the plot as given in the plot history.

```{r, eval=FALSE}
recall_plots(x, ID = 3)
```

**Note** for best results, the R versions should be the same for both creating and recalling the plot.
